### 2016-05-03 ch03-lrm/nonparametric.tex
Structure in LPMtrunc

\subsection{The Local Polynomial Method}
The \gls{LPM} is method that predates the \gls{LRM} and has been devised by~\citet{Schoukens2006LPM}.
The \gls{LPM} approximates both the \gls{FRF} and transient contribution by means of complex-valued local polynomials in the frequency domain.

@@

\section{Conclusion}
\label{sec:conclusion}
In this chapter, the performance of non-parametric \gls{LPM} and \gls{LRM} estimators were compared to observe the \gls{FRF} of resonant systems.
Since the \gls{LRM} is an inherently biased estimator while the \gls{LPM} is asymptotically unbiased, it is important to compare their behavior.
Hence, expressions for the bias of the \gls{LRM} were derived.
%TODO: tom: "inherently biased": verrgaande uitspraak in relatie met Levy: is normaal ook biased, maar voor ARX niet. Hoe zit dat hier?
For good \glspl{SNR} in resonant systems, it was seen that the \gls{LRM} is always superior to the \gls{LPM}.
For extremely poor \gls{SNR}, i.e. $\SNR \approx 10\unit{dB}$, the \gls{LPM} may perform slightly better than the \gls{LRM} when short measurement records are available.
In this chapter, the \gls{LRIC} was introduced.
This is an extension of the \gls{LRM} which solves the non-linear optimization problem and should thus be able to avoid a bias altogether.
However, it is seen that this estimator is extremely noisy but seems to provide a smaller bias than the \gls{LRM}.
Since the overall \gls{RMS} error for the \gls{LRIC} is much larger than most other methods, the \gls{LRIC} cannot be used in its current form.

>>>>

\subsection{The Local Polynomial Method}
\label{sec:nparam:LPM}
The \gls{LPM} is method that predates the \gls{LRM} and has been devised by~\citet{Schoukens2006LPM}.
The \gls{LPM} approximates both the \gls{FRF} and transient contribution by means of complex-valued local polynomials in the frequency domain.

@@

\section{Conclusions}
\label{sec:conclusion}
In this chapter, the performance of non-parametric \gls{LPM} and \gls{LRM} estimators were compared to observe the \gls{FRF} of resonant systems.
Since the \gls{LRM} is a biased estimator while the \gls{LPM} is asymptotically unbiased, it is important to compare their behavior.
Hence, expressions for the bias of the \gls{LRM} were derived.
%TODO: tom: "inherently biased": verregaande uitspraak in relatie met Levy: is normaal ook biased, maar voor ARX niet. Hoe zit dat hier?
For good \glspl{SNR} in resonant systems, it was seen that the \gls{LRM} is always superior to the \gls{LPM}.
For extremely poor \gls{SNR}, i.e. $\SNR \approx 10\unit{dB}$, the \gls{LPM} may perform slightly better than the \gls{LRM} when short measurement records are available.
In this chapter, the \gls{LRIC} was introduced.
This is an extension of the \gls{LRM} which solves the non-linear optimization problem and should thus be able to avoid a bias altogether.
However, it is seen that this estimator is extremely noisy but seems to provide a smaller bias than the \gls{LRM}.
Since the overall \gls{RMS} error for the \gls{LRIC} is much larger than most other methods, the \gls{LRIC} cannot be used in its current form.

### 2016-05-03 ch03-lrm/truncation.tex
Structure in LPMtrunc

The rest of the section is structured as follows. 
\secref{sec:nparam:trunc:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
\secref{sec:nparam:trunc:smoothingFRFestimate} discusses the novel smoothing method.
Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following \gls{FRF} estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\omega_k)$.

@@

% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:blockH0} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
% \begin{equation}\label{lpm1spectra}
% Y(k)=G_0(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
% \end{equation}
% where $V_0(k) = H_0(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\omega_k) = T_G(\omega_k) + T_H(\omega_k)$.

% The smooth characteristics of $G_0(\omega_k)$ and $T(\omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \emph{viz}:
% \begin{align}\label{lpmGTaylorS}
% G_0(\omega_{k+r})&=G_0(\omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
% \bigO{\left(\frac{r}{N}\right)^{R+1}},
% \\
% \label{lpmTTaylorS}
% T(\omega_{k+r})&=T(\omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
% \bigO{  \left(\frac{r}{N}\right)^{R+1}  }
% ,
% \\
% \text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
% \end{align}

@@

% Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \emph{viz}:
% \begin{equation}\label{lpmGTMatrix}
% Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
% \end{equation}
% where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\omega_k)$, $T(\omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
% \begin{align}
% K(k,r) = &\left[
% \begin{matrix}
% U_0(k+r) & U_0(k+r)r & \dots
% \end{matrix}
% \right.
% \\
% &\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
% \end{align}

% Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
% \begin{equation}\label{lpmGTMatrixStack}
% Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
% \end{equation}
% where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
% The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \emph{viz}:
% \begin{align}\label{eq:LSsolutionLPM}
% \hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
% \end{align}

@@

% When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\omega_{k}$:
% \begin{align}
% G_0(\omega_{k+r})
%   &\approx 
%   G_0(\omega_k)+g_1r+g_2r^2
%   \label{eq:lpm:expansionG:quadratic}
% \\
%   T(\omega_{k+r})
%     &\approx 
%     T(\omega_k)+t_1r+t_2r^2
%     \label{eq:lpm:expansionT:quadratic}
% \end{align}
% with ($r\in\mathbb{W}_3$) and the vector of parameters:
% \begin{equation}\label{lpmThetaEst}
% \theta^{\TT}(k)=\left[G_0(\omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
% \end{equation}
% The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \emph{viz}:
% \begin{equation}
% \hat{G}_{\LPM}(\omega_k) = \hat\theta_1(k)
% \end{equation}

\subsubsection{Smoothing the \gls{FRF} estimate}
\label{sec:nparam:trunc:smoothingFRFestimate}
The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:trunc:LPMFRFest}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\omega_k)$.

@@

\item A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.

This action results in smoothing the \gls{LPM} estimate of the \gls{FRF}.
\end{enumerate}

@@

\subsubsection{Obtaining the Impulse Response Function}

The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF} in accordance with equation \eqref{eq:defDFT}, \emph{viz}:
\begin{align}\label{eq:impRespiDFT}
\hat g_{{\LPM}\setminus \mathrm{DC}}(t) 
&= 
\frac{1}{\sqrt{N}}
\sum_{k=1}^{N-1}
\hat G_{\LPM}(\omega_k)e^{\frac{j2\pi kt}{N}}
\end{align}
where the estimated \gls{FRF} in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
\begin{align}
\hat G_{\LPM}(\omega_{N-k}) = \overline{\hat G_{\LPM}(\omega_k)},\ \text{for}\ k=1,\dots,N/2
\end{align}
(with $\conj{\hat G_{\LPM}}$ the complex conjugate of $\hat G_{\LPM}$) to ensure $\hat g_{\LPM}(t)$ to be real.

@@

\subsubsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{sec:nparam:trunc:DCvalueEst}
The correct mean value of the impulse response accounts for (i.e. estimates) the \gls{DC} value of the \gls{FRF}. A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}. %The first is a frequency-domain technique and the second is a time-domain technique.

@@

\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{{\LPM}\setminus \mathrm{DC
}}(t)$ to obtain the improved impulse response $\hat g_{\LPM}(t)$, \emph{viz}:
\begin{align}
\hat g_{\LPM}(t) = \hat g_{{\LPM}\setminus \mathrm{DC}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
\end{align}
\end{enumerate}

@@

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances are the \gls{RMS} value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
  \begin{equation}
    s^2(i) 
    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
    = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     \nullHypothesis &: s^2(i-1) = s^2(i)\\
     \altHypothesis    &: s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise (or assumed to be noise if $i=N_S$), the null hypothesis effectively states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  In particular, the null hypothesis is rejected when the empirical $F$ statistic is high, i.e.
  \begin{equation}
    F \isdef \frac{s^2(i-1)}{s^2(i)} \geq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
  \end{equation}
  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom~\citep{EncyclopediaOfMathematics}.
  In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.

@@

\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
\begin{align}
\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
\end{align}
This is valid, as per \assref{ass:decay90perctime}.

@@

\item
Determine the first time-instant $\truncTime$ at which the estimated exponential gets significantly below the noise floor, \emph{viz}:
\begin{align}\label{eq:truncTimeExpFit}
\truncTime = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
\end{align}
where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found. This is discussed below.

@@

\subsubsection{Simulation Results}
\label{sec:nparam:trunc:simResults}

@@

\subsubsection{Conclusion}
\label{sec:nparam:trunc:conclusion}

>>>>

The rest of the section is structured as follows. 
\secref{sec:nparam:trunc:smoothingFRFestimate} discusses the novel smoothing method.
Ultimately, in \secref{sec:nparam:trunc:simResults}, simulation results of the following \gls{FRF} estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_{\trunc}(\omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_{\LPM}(\omega_k)$.

@@

% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:blockH0} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \latin{viz}:
% \begin{equation}\label{lpm1spectra}
% Y(k)=G_0(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
% \end{equation}
% where $V_0(k) = H_0(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\omega_k) = T_G(\omega_k) + T_H(\omega_k)$.

% The smooth characteristics of $G_0(\omega_k)$ and $T(\omega_k)$ allow for the use of the Taylor series representations at the frequency lines $k+r$ in a frequency domain window of width $2n+1$, with a remainder $\bigO{\left(\frac{r}{N}\right)^{R+1}}$ of the first order Taylor series expansion \citep{Schoukens2009LPM}, \latin{viz}:
% \begin{align}\label{lpmGTaylorS}
% G_0(\omega_{k+r})&=G_0(\omega_k)+\sum_{p=1}^{R}g_p(k)r^p+
% \bigO{\left(\frac{r}{N}\right)^{R+1}},
% \\
% \label{lpmTTaylorS}
% T(\omega_{k+r})&=T(\omega_k)+\sum_{p=1}^{R}t_p(k)r^p+N^{-1/2}
% \bigO{  \left(\frac{r}{N}\right)^{R+1}  }
% ,
% \\
% \text{where}&\ r\in\mathbb{W}_n,\quad \mathbb{W}_n = \{-n,-n+1,\dots,n\}
% \end{align}

@@

% Neglecting the remainder, the Taylor series approximation of \eqref{lpm1spectra} can be written in a matrix vector form, \latin{viz}:
% \begin{equation}\label{lpmGTMatrix}
% Y(k+r)\approx{K(k, r)\theta(k)+V_0(k+r)}
% \end{equation}
% where $\theta(k)\in\mathbb{C}^{2R+2}$ is the column vector of the  parameters ($G_0(\omega_k)$, $T(\omega_k)$, $g_p$, $t_p$, and $p = 1, 2, ...., R$) and $K(k, r)$ is the row vector of their respective coefficients:
% \begin{align}
% K(k,r) = &\left[
% \begin{matrix}
% U_0(k+r) & U_0(k+r)r & \dots
% \end{matrix}
% \right.
% \\
% &\quad\left.\begin{matrix}U_0(k+r)r^R & 1& r&\dots&r^R\end{matrix}\right]\nonumber
% \end{align}

% Equation \eqref{lpmGTMatrix} can be written in the more compact (stacked vectors) form:
% \begin{equation}\label{lpmGTMatrixStack}
% Y_n(k)\approx K_n(k)\theta(k)+V_n(k)
% \end{equation}
% where $Y_n(k), V_n(k)\in\mathbb{C}^{2n+1}$, and $K_n(k)\in\mathbb{C}^{(2n+1)\times(2R+2)}$ are the stacked values of $Y(k+r)$, $K(k,r)$, and $V_0(k+r)$, respectively, for $r\in\mathbb{W}_n$.
% The estimates of the parameters $\theta(k)$ are obtained as the minimizers of the least squares problem, \latin{viz}:
% \begin{align}\label{eq:LSsolutionLPM}
% \hat\theta(k) = \argmin_{\theta(k)} \left\|Y_n(k) - K_n(k)\theta(k)\right\|_2^2
% \end{align}

@@

% When substituted into equations \eqref{lpmGTaylorS} and \eqref{lpmGTMatrix},  these yield the following quadratic local polynomials of $G_0$ and $T$ around a central frequency $\omega_{k}$:
% \begin{align}
% G_0(\omega_{k+r})
%   &\approx 
%   G_0(\omega_k)+g_1r+g_2r^2
%   \label{eq:lpm:expansionG:quadratic}
% \\
%   T(\omega_{k+r})
%     &\approx 
%     T(\omega_k)+t_1r+t_2r^2
%     \label{eq:lpm:expansionT:quadratic}
% \end{align}
% with ($r\in\mathbb{W}_3$) and the vector of parameters:
% \begin{equation}\label{lpmThetaEst}
% \theta^{\TT}(k)=\left[G_0(\omega_k) \ g_1 \ g_2\  T_G(k)\  t_1 \ t_2\right]
% \end{equation}
% The \gls{LPM} estimate of the \gls{FRF} is the first element of the estimate $\hat\theta(k)$, obtained from \eqref{eq:LSsolutionLPM}, \latin{viz}:
% \begin{equation}
% \hat{G}_{\LPM}(\omega_k) = \hat\theta_1(k)
% \end{equation}

\subsection{Smoothing the \gls{FRF} estimate}
\label{sec:nparam:trunc:smoothingFRFestimate}
The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:LPM}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\omega_k)$.

@@

\item A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
This action results in smoothing the \gls{LPM} estimate of the \gls{FRF}.
\end{enumerate}

@@

\subsection{Obtaining the Impulse Response Function}

The estimated impulse response function  $\hat g_{{\LPM}\setminus \mathrm{DC}}(t)$ is obtained explicitly via the \gls{IDFT} of the \gls{LPM}-estimate $\hat G_{\LPM}(\omega_k)$ of the \gls{FRF}, \latin{viz}:
\begin{align}\label{eq:impRespiDFT}
\hat g_{{\LPM}\setminus \mathrm{DC}}(t) 
&= 
\frac{1}{\sqrt{N}}
\sum_{k=1}^{N-1}
\hat G_{\LPM}(\omega_k)e^{\frac{j2\pi kt}{N}}
\end{align}
where the estimated \gls{FRF} in the frequency band between  the Nyquist and the sample frequencies is obtained as follows:
\begin{align}
\hat G_{\LPM}(\omega_{N-k}) = \overline{\hat G_{\LPM}(\omega_k)},\ \text{for}\ k=1,\dots,N/2
\end{align}
(with $\conj{\hat G_{\LPM}}$ the complex conjugate of $\hat G_{\LPM}$) to ensure $\hat g_{\LPM}(t)$ to be real.

@@

\subsection{Estimating the \glsentrytext{DC} Value of the \glsentrytext{FRF}}\label{sec:nparam:trunc:DCvalueEst}
The correct mean value of the impulse response accounts for (i.e. estimates) the \gls{DC} value of the \gls{FRF}. A time-domain method is proposed for estimating the mean value of the impulse response in equation \eqref{eq:impRespiDFT}. %The first is a frequency-domain technique and the second is a time-domain technique.

@@

\item Next, subtract the computed mean value $m_{g10}$ from $\hat g_{{\LPM}\setminus \mathrm{DC
}}(t)$ to obtain the improved impulse response $\hat g_{\LPM}(t)$, \latin{viz}:
\begin{align}
\hat g_{\LPM}(t) = \hat g_{{\LPM}\setminus \mathrm{DC}}(t) - m_{g10},\ \text{for}\ t=0,1,\dots,N-1
\end{align}
\end{enumerate}

\subsection{Determining the Truncation Time}
In this section, two methods will be discussed to determine the truncation time, i.e. the time beyond which the measured impulse response cannot be separated from the noise level.
Specifically, the first method uses an $F$-test to distinguish between signal and noise.
The second method fits an exponential through a well-chosen subset of the data to obtain $\truncTime$.

@@

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances are the \gls{RMS} value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \latin{viz}:
  \begin{equation}
    s^2(i) 
    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
    = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     \nullHypothesis &: s^2(i-1) = s^2(i)\\
     \altHypothesis    &: s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise (or assumed to be noise if $i=N_S$), the null hypothesis effectively states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  In particular, the null hypothesis is rejected when the empirical $F$ statistic is high, i.e.
  \begin{equation}
    F \isdef \frac{s^2(i-1)}{s^2(i)} \geq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
  \end{equation}
  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom~\citep{EncyclopediaOfMathematics}.
  In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.

@@

\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \latin{viz}:
\begin{align}
\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
\end{align}
This is valid, as per \assref{ass:decay90perctime}.

@@

\item
Determine the first time-instant $\truncTime$ at which the estimated exponential gets significantly below the noise floor, \latin{viz}:
\begin{align}\label{eq:truncTimeExpFit}
\truncTime = \min \left\{t:Ae^{at} < \gamma\hat\sigma_\mathrm{n}\right\}
\end{align}
where the parameter $\gamma$ can be tuned such that an appropriate trade-off between the decreased variance and the increased bias on the estimated smoothed FRF is found. This is discussed below.

@@

\subsection{Simulation Results}
\label{sec:nparam:trunc:simResults}

@@

\subsection{Conclusion}
\label{sec:nparam:trunc:conclusion}
